\textbf{The Illusion Game: A Novel Experimental Paradigm Provides Evidence in Favour of a General Factor of Visual Illusion Sensitivity and Personality Correlates}

### 2022-09-06 manuscript.Rmd
Revert "format"
This reverts commit 11b12c954a47422c0fa46f988006c86bf6450300.

The effect on errors was monotonic for most illusions, with the exception of Delboeuf and Zöllner. For both of them, mildly congruent illusion strengths (which theoretically were supposed to be associated with less errors than incongruent effects) were related to a small and strong increase of errors, respectively. Forthe Delboeuf illusion, we believe that this was due to an artifact caused by the illusion generation algorithm: the outline of the target circles was always created as slightly bigger, which made the difference between them more obvious at an illusion strength of 0. This was fixed in latest release of *Pyllusion* (v1.2), which now generate outlines of the same size as the target circle. For the Zöllner illusion, however, this observation is consistent with the findings of [@kitaoka2000], who reported an acute angle contraction effect at large angles (50 to 90 degrees) between the target horizontal line and the biasing horizontal bars. Although the Zollner illusion is commonly thought to be driven by an acute angle expansion mechanism that is optimal at small angles (below 30 degrees), an indirect illusory effect can be observed at sufficiently large angles due to the opposing acute angle contraction mechanism invoked [@kitaoka2007; @kitaoka2000a].

>>>>

The effect on errors was monotonic for most illusions, with the exception of Delboeuf and Zöllner. For both of them, mildly congruent illusion strengths (which theoretically were supposed to be associated with less errors than incongruent effects) were related to a small and strong increase of errors, respectively. Forthe Delboeuf illusion, we believe that this was due to an artifact caused by the illusion generation algorithm: the outline of the target circles was always created as slightly bigger, which made the difference between them more obvious at an illusion strength of 0. This was fixed in latest release of *Pyllusion* (v1.2), which now generate outlines of the same size as the target circle. For the Zöllner illusion, however, this observation is consistent with the findings of [@kitaoka2000], who reported an acute angle contraction effect at very small as well as at sufficiently large angles (below 10 degrees for the former and between 50 to 90 degrees for the latter) between the target horizontal line and the biasing horizontal bars when the illusion strength is weak. This invoked underlying acute angle contraction mechanism could hence potentially explain the indirect illusory effect observed [@kitaoka2007; @kitaoka2000a].
